Kids SUMs Summary

### 2020-01-23 stove_grade_usage_summary.Rmd
data cleaning

---
title: "Kids stove grades and usage summary"
author: "Ethan Walker"
date: "Started 15 Jan 2020, Updated 15 Jan 2020"
output: pdf_document
---

@@

# Summarize factor vars
## Use this as a quick look at all vars
table_list <- stove_use_clean %>% 
  #filter(area == "WMT") %>% 
  filter(winter_id == 1) %>% 
  select(-home_winter_id, -wood_cords, -wood_type_other,
         -home_id, -home, -treatment) 
lapply(table_list, table)
```

# Summary of stove grades
```{r}
## Look further into NA values? ##
stove_grade_summary <- stove_grades_clean %>% 
  filter(winter_id == 1 | winter_id == 2) %>% 
  select(area, home, stove_grade) %>% 
  filter(!is.na(stove_grade)) %>% 
  group_by(area, stove_grade) %>% 
  distinct(home) %>% 
  summarize(n())
kable(stove_grade_summary, align = "c")
```

@@

# Summary of stove use
```{r}
# Summarize numeric vars
stove_use_summary <- stove_use_clean %>% 
  group_by(area) %>% 
  summarize("N" = n(),
            "Mean Cords" = mean(wood_cords, na.rm = TRUE),
            "SD Cords" = sd(wood_cords, na.rm = TRUE),
            "Min Cords" = min(wood_cords, na.rm = TRUE), 
            "Median Cords" = median(wood_cords, na.rm = TRUE), 
            "Max Cords" = max(wood_cords, na.rm = TRUE))
kable(stove_use_summary, digits = 1, align = "c")

@@

stove_use_plot <- data %>% 
  select(area, variable) %>% 
  rename(plot_var = variable) %>% 
  #na.exclude() %>% 
  ggplot() +
    geom_bar(aes(plot_var, fill = area)) +
    theme_minimal() +
    labs(title = variable) +
    theme(axis.text.x = element_text(size = 16, colour = "black", 
                                     angle = 40, vjust = 0.7, hjust = 0.7),
          axis.text.y = element_text(size = 16, colour = "black"),
          legend.text = element_text(size = 14, colour = "black"),
          legend.title = element_text(size = 16, colour = "black"),
          title = element_text(size = 18, colour = "black"),
          axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(),
          panel.grid = element_blank()) +
    scale_fill_manual(values = jv_palette)
stove_use_plot

>>>>

---
title: "Kids stove grades and usage summary"
author: "Ethan Walker"
date: "Started 15 Jan 2020, Updated 23 Jan 2020"
output: pdf_document
---

@@

# Summarize factor vars
## Use this as a quick look at all vars
table_list <- stove_use_clean %>% 
  #filter(area == "WMT") %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>%  
  select(-home_winter_id, -wood_cords, -wood_type_other,
         -home_id, -home, -treatment) 
lapply(table_list, table)
```

# Summary of stove grades
```{r}
## Look further into NA values? ##
stove_grade_summary <- stove_grades_clean %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  select(area, home, stove_grade) %>% 
  #filter(!is.na(stove_grade)) %>% 
  group_by(area, stove_grade) %>% 
  distinct(home) %>% 
  summarize(n())
kable(stove_grade_summary, align = "c")
```

@@

# Summary of stove use
```{r}
# Summarize numeric vars
stove_use_summary <- stove_use_clean %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  group_by(area) %>% 
  summarize("N" = n(),
            "Mean Cords" = mean(wood_cords, na.rm = TRUE),
            "SD Cords" = sd(wood_cords, na.rm = TRUE),
            "Min Cords" = min(wood_cords, na.rm = TRUE), 
            "Median Cords" = median(wood_cords, na.rm = TRUE), 
            "Max Cords" = max(wood_cords, na.rm = TRUE))
kable(stove_use_summary, digits = 1, align = "c")

@@

stove_use_plot <- data %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  select(area, variable) %>% 
  rename(plot_var = variable) %>% 
  #na.exclude() %>% 
  ggplot() +
    geom_bar(aes(plot_var, fill = area)) +
    theme_minimal() +
    labs(title = variable) +
    theme(axis.text.x = element_text(size = 16, colour = "black", 
                                     angle = 40, vjust = 0.7, hjust = 0.7),
          axis.text.y = element_text(size = 16, colour = "black"),
          legend.text = element_text(size = 14, colour = "black"),
          legend.title = element_text(size = 16, colour = "black"),
          title = element_text(size = 18, colour = "black"),
          axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(),
          panel.grid = element_blank()) +
    scale_fill_manual(values = jv_palette)
stove_use_plot

### 2020-01-23 sums_data_cleaning.Rmd
data cleaning

sums_time_trends_plot <- sums_clean %>% 
  filter(home == "WMA102") %>% 
  ggplot() + 
    geom_point(aes(datetime_sums, temp_c_sums, color = month_sums), size = 1.5) +
    theme_classic() +
    labs(y = "Temperature (degrees C)",
         x = "Datetime",
         color = "Month of Year") +
    theme(axis.title.y = element_text(size = 12,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.title.x = element_text(size = 12),
          axis.text.x = element_blank(),
          axis.text.y = element_text(size = 12, color = "black"),
          axis.line.x = element_line(colour = "black", size = 1), 
          axis.line.y = element_line(colour = "black", size = 1), 
          axis.ticks = element_blank()) +
    scale_color_manual(values = jv_palette)
sums_time_trends_plot
```

@@

>>>>

sums_time_trends_plot <- sums_clean %>% 
  filter(home == "CH405") %>% 
  ggplot() + 
    geom_point(aes(datetime_sums, temp_c_sums, color = month_sums), size = 1.5) +
    theme_classic() +
    labs(y = "Temperature (degrees C)",
         x = "Datetime",
         color = "Logtag ID") +
    theme(axis.title.y = element_text(size = 12,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.title.x = element_text(size = 12),
          axis.text.x = element_blank(),
          axis.text.y = element_text(size = 12, color = "black"),
          axis.line.x = element_line(colour = "black", size = 1), 
          axis.line.y = element_line(colour = "black", size = 1), 
          axis.ticks = element_blank()) +
    scale_color_manual(values = jv_palette)
sums_time_trends_plot
```

@@

# Thresholds for heating events
```{r}
# Load SUMs data
sums_clean <- read_rds("Output/sums_clean.rds")

thresholds <- sums_clean %>% 
  group_by(area, home, winter_id) %>%
  mutate(temp_sums_40 = if_else(temp_c_sums >= 40, 1, 0),
         temp_sums_40_event = if_else(temp_sums_40 == 1 & lag(temp_sums_40) == 0, "Start", "Null"),
         temp_sums_40_event = if_else(is.na(temp_sums_40_event), "Start", temp_sums_40_event),
         temp_sums_40_event = if_else(temp_sums_40 == 1 & temp_sums_40_event == "Null",
                                      "Event", temp_sums_40_event),
         temp_sums_40_event = if_else(temp_sums_40_event == "Event" &
                                      lead(temp_sums_40_event) == "Null" &
                                      lead(temp_sums_40_event, 2) == "Null" &
                                      lead(temp_sums_40_event, 3) == "Null", "End", temp_sums_40_event)) %>% 
  group_by(area, home, winter_id, date_sums, temp_sums_40_event) %>% 
  summarize(n = n()) %>% 
  group_by(temp_sums_40_event) %>% 
  summarize(mean(n))

table(thresholds$temp_sums_40_event)
```

### 2020-01-23 sums_summary.Rmd
data cleaning

---
title: "Kids SUMs Summary"
author: "Ethan Walker"
date: "Started 9 Jan 2020, Updated 15 Jan 2020"
output: pdf_document
---

@@

# Summary stats by area (winter)
```{r}
sums_summary <- sums_clean %>% 
  # group by: area, treatment, dtid, day_of_week, Sampling_day
  group_by(area, winter_id) %>% 
  summarize("n" = n(),
            "Mean Temp" = mean(temp_c_sums, na.rm = TRUE), 
            "SD Temp" = sd(temp_c_sums, na.rm = TRUE),
            "Min Temp" = min(temp_c_sums, na.rm = TRUE), 
            "Median Temp" = median(temp_c_sums, na.rm = TRUE),
            "Max Temp" = max(temp_c_sums, na.rm = TRUE)) %>% 
  select(-area, -winter_id) %>% 
  t()

kable(sums_summary, col.names = c("Alaska (1)", "Alaska (2)",
                                  "Navajo (1)", "Navajo (2)",
                                  "Montana (1)", "Montana (2)"), 
      digits = 1, align = "c")
```

# Boxplots for SUMs temp (C) by study area - Winter 1
```{r, fig.height=6, fig.width=5}
boxplots_kids_sums <- sums_clean %>%
  filter(winter_id == 1) %>% 
  ggplot(aes(area, temp_c_sums)) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    stat_summary(fun.y=mean, geom="point", shape=17, size=3, color="red") +
    theme_minimal() +
    ylim(-50, 100) +
    #geom_hline(yintercept = 50, color = "red", size = 1.2) +
    labs(y = "Temperature (degrees C)") +
    #labs(aes(x = "", y = paste("48-hour indoor PM "[2.5], " (", mu, g/m^3, ")"))) +
    theme(axis.text.x = element_text(size = 16, colour = "black"),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank())
boxplots_kids_sums
```

>>>>

---
title: "Kids SUMs Summary"
author: "Ethan Walker"
date: "Started 9 Jan 2020, Updated 23 Jan 2020"
output: pdf_document
---

@@

# Summary stats by area (winter)
```{r}
sums_summary <- sums_clean %>% 
  # group by: area, treatment, dtid, day_of_week, Sampling_day
  #filter(winter_id == 1 & treatment == "Placebo") %>% 
  filter(temp_c_sums <= 0) %>% 
  group_by(area, home, ibid) %>% 
  summarize("n" = n(),
            "Mean Temp" = mean(temp_c_sums, na.rm = TRUE), 
            "SD Temp" = sd(temp_c_sums, na.rm = TRUE),
            "Min Temp" = min(temp_c_sums, na.rm = TRUE), 
            "Median Temp" = median(temp_c_sums, na.rm = TRUE),
            "Max Temp" = max(temp_c_sums, na.rm = TRUE)) %>% 
  select(-area) %>% 
  t()

kable(sums_summary, col.names = c("Alaska", "Navajo", "Montana"), digits = 1, align = "c")

sums_summary <- sums_clean %>% 
  # group by: area, treatment, dtid, day_of_week, Sampling_day
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  filter(temp_c_sums > 0) %>% 
  group_by(area) %>% 
  summarize("n" = n(),
            "Mean Temp" = mean(temp_c_sums, na.rm = TRUE), 
            "SD Temp" = sd(temp_c_sums, na.rm = TRUE),
            "Min Temp" = min(temp_c_sums, na.rm = TRUE), 
            "Median Temp" = median(temp_c_sums, na.rm = TRUE),
            "Max Temp" = max(temp_c_sums, na.rm = TRUE)) %>% 
  select(-area) %>% 
  t()

kable(sums_summary, col.names = c("Alaska", "Navajo", "Montana"), digits = 1, align = "c")
```

# Boxplots for SUMs temp (C) by study area - Winter 1
```{r, fig.height=6, fig.width=5}
boxplots_kids_sums <- sums_clean %>%
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  ggplot(aes(area, temp_c_sums)) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    stat_summary(fun.y=mean, geom="point", shape=17, size=3, color="red") +
    theme_minimal() +
    ylim(-50, 100) +
    #geom_hline(yintercept = 50, color = "red", size = 1.2) +
    labs(y = "Temperature (degrees C)") +
    #labs(aes(x = "", y = paste("48-hour indoor PM "[2.5], " (", mu, g/m^3, ")"))) +
    theme(axis.text.x = element_text(size = 16, colour = "black"),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank())
boxplots_kids_sums
```
